### 2016-02-11 inputs/conclusions.tex
conclusions+table

\textcolor{red}{TO BE DELETED?\\Exploring ways to improve imputation accuracy in GBS data, for instance by combining predictive methods as in boosting or model ensembling, while at the same time increasing algorithm efficiency to keep computation times reasonably low, is an important research area, and can help making low-cost genotyping-by-sequencing a very cost-effective technique for genomic applications in species with and without a reference genome.}

Exploring ways to improve imputation accuracy in GBS data is an important research area and can help making genotyping-by-sequencing a very cost-effective technique. In this paper we shown how general imputation algorithms are a valid alternative to genotype-oriented ones when reference genomes are not available or too expensive in terms of unaligned markers. Moreover, we highlighted the importance of examining the accuracy on minority classes, since the common practice of summarizing performances in a single index can easily mislead to undesired results.

>>>>

%Exploring ways to improve imputation accuracy in GBS data, for instance by combining predictive methods as in boosting or model ensembling, while at the same time increasing algorithm efficiency to keep computation times reasonably low, is an important research area, and can help making low-cost genotyping-by-sequencing a very cost-effective technique for genomic applications in species with and without a reference genome.}

The results of this paper showed that high imputation accuracies can be achieved with GBS data, and that general imputation methods are a valid option when the reference genome is not available or the alignment on the genome of a closely related species leads to losing too many markers. Additionally, we highlighted the importance of examining imputation accuracy in the different genotype classes, since the common practice of summarizing performances in a single index can be very misleading when data are unbalanced (i.e. MAF is low).
Exploring ways to improve imputation accuracy in GBS data is an important research area and can help making genotyping-by-sequencing a very attractive and cost-effective technique for genomic applications in species with and without a reference genome.

### 2016-02-11 inputs/table_accuracies.tex
conclusions+table

\begin{table}
\centering
\caption[Accuracy statistics]{Imputation accuracies (as percentages) for the various
datasets and methods, averaged over all allowed and injected missing thresholds. Rice data are reported averaged by chromosome and on the complete genotypes. Alfalfa data are reported averaged over the two Alfalfa-PV and Alfalfa-Med populations. FILLIN failed to impute alfalfa datasets.}
\label{tab:accuracy_statistics}
\begin{tabular}{llcccc}
\hline\noalign{\smallskip}
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Dataset} & \textbf{Method} & \textbf{Total} & \textbf{Minor (BB)} & \textbf{Major (AA)} & \textbf{Heterozygote (AB)}\\
\noalign{\smallskip}\Xhline{3\arrayrulewidth}\noalign{\smallskip}
alfalfa & Beagle & 73.14 & 14.27 & 99.37 & 20.77\\
alfalfa & Beagle (shuffle) & 66.34 & 1.31 & 99.88 & 0.50\\
alfalfa & kNNI & 82.20 & 14.68 & 90.82 & 66.03\\
alfalfa & MNI & 78.38 & 0.00 & 88.69 & 58.88\\
alfalfa & RFI  & 79.50 & 0.01 & 89.05 & 61.75\\
alfalfa & SVDI & 77.36 & 4.47 & 85.81 & 61.67\\
alfalfa & FILLIN & * & * & * & -\\
alfalfa & FILLIN (shuffle)  & * & * & * & -\\
rice (chr) & Beagle & 99.58 & 97.50 & 99.80 & -\\
rice (chr) & Beagle (shuffle) & 96.09 & 74.73 & 98.42 & -\\
rice (chr) & kNNI & 98.10 & 89.12 & 99.04 & -\\
rice (chr) & MNI & 90.19 & 1.06 & 99.89 & -\\
rice (chr) & RFI  & 98.81 & 91.51 & 99.58 & -\\
rice (chr) & SVDI & 97.81 & 85.64 & 99.11 & -\\
rice (chr) & FILLIN & 86.96 & 63.62 & 90.14 & -\\
rice (chr) & FILLIN (shuffle)  & 82.19 & 55.86 & 85.81 & -\\
rice & Beagle & 99.58 & 97.57 & 99.80 & -\\
rice & Beagle (shuffle) & 93.48 & 55.64 & 97.69 & -\\
rice & kNNI & 98.30 & 89.80 & 99.19 & -\\
rice & MNI & 90.21 & 0.61 & 99.89 & -\\
rice & RFI  & 97.86 & 84.68 & 99.28 & -\\
rice & SVDI & 95.74 & 70.96 & 98.40 & -\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\centering
\caption[Accuracy statistics]{Imputation accuracies (as percentages) for the various
datasets and methods, averaged over all allowed and injected missing thresholds. Rice data are reported averaged by chromosome and on the complete genotypes. Alfalfa data are reported averaged over the two Alfalfa-PV and Alfalfa-Med populations. FILLIN failed to impute alfalfa datasets.}
\label{tab:accuracy_statistics}
\begin{tabular}{llcccc}
\hline\noalign{\smallskip}
\noalign{\smallskip}\hline\noalign{\smallskip}
\textbf{Dataset} & \textbf{Method} & \textbf{Total} & \textbf{Minor (BB)} & \textbf{Major (AA)} & \textbf{Heterozygote (AB)}\\
\noalign{\smallskip}\Xhline{3\arrayrulewidth}\noalign{\smallskip}
alfalfa & Beagle & 73.14 & 14.27 & 99.37 & 20.77\\
alfalfa & Beagle (shuffle) & 66.34 & 1.31 & 99.88 & 0.50\\
alfalfa & kNNI & 82.20 & 14.68 & 90.82 & 66.03\\
alfalfa & MNI & 78.38 & 0.00 & 88.69 & 58.88\\
alfalfa & RFI  & 79.50 & 0.01 & 89.05 & 61.75\\
alfalfa & SVDI & 77.36 & 4.47 & 85.81 & 61.67\\
alfalfa & FILLIN & * & * & * & *\\
alfalfa & FILLIN (shuffle)  & * & * & * & *\\
rice (chr) & Beagle & 99.58 & 97.50 & 99.80 & -\\
rice (chr) & Beagle (shuffle) & 96.09 & 74.73 & 98.42 & -\\
rice (chr) & kNNI & 98.10 & 89.12 & 99.04 & -\\
rice (chr) & MNI & 90.19 & 1.06 & 99.89 & -\\
rice (chr) & RFI  & 98.81 & 91.51 & 99.58 & -\\
rice (chr) & SVDI & 97.81 & 85.64 & 99.11 & -\\
rice (chr) & FILLIN & 86.96 & 63.62 & 90.14 & -\\
rice (chr) & FILLIN (shuffle)  & 82.19 & 55.86 & 85.81 & -\\
rice & Beagle & 99.58 & 97.57 & 99.80 & -\\
rice & Beagle (shuffle) & 93.48 & 55.64 & 97.69 & -\\
rice & kNNI & 98.30 & 89.80 & 99.19 & -\\
rice & MNI & 90.21 & 0.61 & 99.89 & -\\
rice & RFI  & 97.86 & 84.68 & 99.28 & -\\
rice & SVDI & 95.74 & 70.96 & 98.40 & -\\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
